\input{header}

\begin{document}

 \hspace{-8.5em} { \Large \robotoslab Giulio Luzzati, Ph.D.}% Your name at the top
 \vspace{-0.5em}

\moveleft\hoffset\vbox{\color{color1}\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
\vspace{-2em}
%----------------------------------------------------------------------------------------

\begin{resume}
\robotoslab

\section{Personal Information}
Principal DSP Engineer\\
{\robotocondensed 1b Mill Road, Haddenham, Ely} \\
Phone: {\robotocondensed +44 07397 791131}\\
e-mail: {\robotocondensed giulio.luzzati@live.it}\\
LinkedIn: {\url{https://it.linkedin.com/in/giulio-luzzati-9bb79245}}\\
Born: 19/10/1984, Genova, Italy
\vspace{-1em}
\section{In a\\Nutshell}~
\expbox{I am a software engineer with a strong scientific background. My drive is to design and analyse systems, understand what makes them tick and how they could be better. I strive to frame my actions within the bigger picture, and I have a track record of delivering solid, dependable, and (re)usable solutions.}
\vspace{-1em}
\section{Education}
\textbf{University of Genova,} Genova, Italy\\
\cvitem{Ph.D. in Computer Science}{Apr 2016}\vspace{-1em}\\
\small Thesis topics: resource allocation, communication networks, signal processing \normalsize\\
\cvitem{Professional Engineering Qualification}{Oct 2012}\vspace{-1em}\\
\cvitem{M.Sc. in Telecommunication Engineering}{May 2012}\vspace{-1em}\\	
\vspace{-1em}
\section{Professional \\and Academic Experience} 
\textbf{Cambridge Touch Technologies (CTT)}, Cambridge, United Kingdom\\
\cvitem{Principal DSP Engineer}{Oct 2018 - Current}
\expbox{CTT is a touch screen technology startup, providing cost effective ways to add touch-pressure sensing capabilities to display and non-display surfaces. 
At CTT my main responsibilities are to productize DSP algorithms and software, optimize the team's processes, mentor the team for best practices, participate in technology strategy meetings.
Over the years I've set up the company's sw development and deployment workflow, as well as the testing/CI automation infrastructure.}

\textbf{5G Innovation Centre}, Guildford, United Kingdom\\
\cvitem{Senior Software Engineer}{Nov 2017 - Oct 2018}
\expbox{The 5GIC is a research centre within the University of Surrey, featuring one of the biggest 5G testbeds in the UK and carrying on research and standardization activity in close partnership with some of the largest players in the field. The 5GIC's testbed, a complete cellular network, showcases several research ideas, from the physical layer to network concepts.
At the 5GIC I was part of the core network team. My contribution as a software engineer was to develop and maintain the codebase for the core network.}

\textbf{AKYA ltd}, Swindon, United Kingdom\\
\cvitem{DSP Software Engineer}{Dec 2016 - Nov 2017}
\expbox{AKYA's core business was a novel ``dynamically reconfigurable logic'' approach to hardware design, for low power/low cost applications, unlike e.g. FPGA, providing ``just enough'' reconfigurability to meet design requirements. 
At AKYA I contributed as a software engineer to develop a framework that synthesises RT logic from a high-level description of the hardware. My role was to design and develop algorithms and software components that expand and integrate the existing framework, as well as creating tools for testing and data visualization.}

\textbf{DSP Lab, University of Genova}, Genova, Italy\\
\cvitem{Post Doctoral Research Fellow}{Jan 2016 - Nov 2016}
\cvitem{Ph.D. Student}{Jan 2013 - Dec 2015}
\cvitem{Research Fellow}{Oct 2012 - Dec 2012}
\expbox{During my academic experience at the DSP Labs, as Ph.D. student and then research fellow, I carried out academic (research and teaching) activity, along with projects in collaboration with SMEs and some of the key industries of Italy's communications and tech (Telecom Italia, Leonardo). My main area of research were resource allocation and mathematical optimization in communication networks and in signal processing}
% \textbf{National Council of Research (CNR)}, Genova, Italy\\
%{\sl Internship, ISSIA group,  Bachelor Thesis research. } \hfill{\bf  2008}
\pagebreak


\section{Technical \\Skills}
\begin{tabular}{cc}
\skillc{C}&
\skillb{C++}\\
\skillc{Python}&
\skillb{Matlab}\\
\skillb{Latex}&
\skillb{Shell}\\
\end{tabular}

\footnotesize
\begin{tabular}{lll}
Software Architecture & Build Systems & CI, DevOps \\
Containerization & Embedded Programming & Basic Hardware Diagnostics \\
Automated Testing & Agile Software Development & GNU/Linux OS \\
\end{tabular}
\normalsize

\section{Scientific \\Skills}
\footnotesize
\begin{tabular}{l}
Signal processing\\
Computer networks\\
Statistics, data science \\
Mathematical optimization \\
Working knowledge in machine learning \\
\end{tabular}
\normalsize

\section{Relevant \\Projects}
\input{projects/dianne}\vspace{-1em}
\input{projects/hfm}\vspace{-1em}
\input{projects/stockholm}\vspace{-1em}
\input{projects/ian}\vspace{-1em}
\input{projects/qhm}\vspace{-1em}

%\hfill
%\small
\pagebreak
%\input{publications}

\end{resume}
\end{document}
