\input{header}
\newcommand{\printversion}{\color{gray!10}\cvversion}  % Light gray, very small text
\newcommand\keyword[2][]{\tikz[overlay]\node[fill=color1!10,inner sep=1.8pt, anchor=text, rectangle, rounded corners=1.2mm, #1] {#2};\phantom{#2}}

\begin{document}

 \hspace{-8.5em} { \Large \robotoslab Giulio Luzzati, Ph.D.}% Your name at the top
 \vspace{-0.5em}

\moveleft\hoffset\vbox{\color{color1}\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
\vspace{-2em}
%----------------------------------------------------------------------------------------

\begin{resume}
\robotoslab

\section{Personal Information}
{\robotocondensed 1b Mill Road, Haddenham, Ely} \\
Phone: {\robotocondensed +44 07397 791131, +39 3756888072}\\
E-mail: {\robotocondensed giulio.luzzati@live.it}\\
LinkedIn: {\url{https://it.linkedin.com/in/giulio-luzzati-9bb79245}}\\
Citizenship: Italian
\vspace{-1em}
\section{In a\\Nutshell}~
\expbox{
My biggest drive is to build things and tools - I work hands-on to build systems that extract information from noisy, complex data.

What I bring to the table is a broad, full-stack approach that extends beyond just algorithmic performance, to encompass the complete iteration cycle: quality assurance, automated build processes, testing, and deployment.

I have good familiarity with electronics and am happy to reach for an oscilloscope to debug, troubleshoot, and validate assumptions.
}
\vspace{-0.1em}
\moveleft\hoffset\vbox{\color{color1}\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
\vspace{-0.5em}

\section{Languages \\and Tools}
\begin{tabular}{lll}
\skillc{C}&
\skilla{C++}&
\skillc{Python}\\
\skillb{Matlab}&
\skillb{Pytorch}&
\skillb{Shell}\\
\skilla{JS}&
\skillc{git}&
\skillb{Docker}\\
\end{tabular}

\section{Scientific \\Skills}
\footnotesize
\begin{tabular}{cc}
\keyword{Signal processing}&
\keyword{Computer networks} \\
\keyword{Data science} &
% \keyword{Mathematical optimization} \\
\keyword{Machine learning}
\end{tabular}
\normalsize

% \vspace{0.25em}
\section{Technical \\Skills}
\footnotesize
\begin{tabular}{ccc}
\keyword{Software Architecture} & \keyword{Data Pipelines} & \keyword{CI, DevOps} \\
\keyword{Embedded Programming} & \keyword{Debugging} & \keyword{GNU/Linux OS} \\
\keyword{Microservices} & ~ & ~ \\
\end{tabular}
\normalsize


\section{Education}
\textbf{University of Genova,} Genova, Italy\\
\cvitem{Ph.D. in Computer Science}{Apr 2016}\vspace{-1em}\\
\small Thesis topics: resource allocation, communication networks, signal processing \normalsize\\
\cvitem{Professional Engineering Qualification}{Oct 2012}\vspace{-1em}\\
\cvitem{M.Sc. in Telecommunication Engineering}{May 2012}\vspace{-1em}\\

\vspace{-1em}
\moveleft\hoffset\vbox{\color{color1}\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
\vspace{-1em}

\section{Professional \\and Academic Experience}

\textbf{Cambridge Touch Technologies (CTT)}, Cambridge, United Kingdom\\
\cvitem{DSP Team Leader}{Jan 2022 - currently}
\cvitem{Principal DSP Engineer}{Jul 2021 - Dec 2021}
\cvitem{Senior DSP Engineer}{Oct 2018 - Jun 2021}
\expbox{CTT is a tech scale-up developing cost-effective touch-pressure sensing for display and non-display surfaces.

Starting with embedded implementation of core algorithms, my role expanded to full-stack responsibilities and workflow integration.
I then gradually pivoted towards a lead role, where alongside ensuring development of the core libraries, I've been working cross-disciplinarily to advance the technology into new experimental applications.

As a team leader, I now translate company strategy into team goals, clear roadblocks and ensure knowledge transfer across teams.
I strive to focus team coordination on key expectations, maximizing members' decisional autonomy.

Some achievements and contributions
\begin{itemize}
 \item Several algorithm proof-of-concepts
 \item I've set up the software versioning and CI infrastructure, based on the Gitlab platform and a state of the art dockerised build/test environments on an on-prem cloud
 \item Created several real-time visualisations and tools to demonstrate, familiarise with, and tune DSP algorithms, using popular Python graphic / game libraries
 \item Built an internal microservice ecosystem that defines and automates the full lifecycle of our algorithm libraries, from code development to chip provisioning. Technologies include Python FastAPI, Artifactory, PostgreSQL, Docker
 \item Built data / ETL pipelines and dashboards to streamline and scale up the analysis and exploration of large datasets
\end{itemize}

}
\pagebreak
\section{Professional \\and Academic Experience\\(cont'd)}

\textbf{5G Innovation Centre}, Guildford, United Kingdom\\
\cvitem{Senior Software Engineer}{Nov 2017 - Oct 2018}
\expbox{The 5GIC is a research centre within the University of Surrey, featuring one of the biggest 5G testbeds in the UK with research and standardization activity in close partnership with some of the largest players in the field. The 5GIC's testbed, a complete cellular network, showcases several research ideas, from the physical layer to network concepts.
At the 5GIC I was part of the core network team. My contribution as a software engineer was to develop and maintain the codebase for the core network.}
\vspace {1em}
\textbf{AKYA ltd}, Swindon, United Kingdom\\
\cvitem{DSP Software Engineer}{Dec 2016 - Nov 2017}
\expbox{AKYA's core business was a novel ``dynamically reconfigurable logic'' approach to hardware design, for low power/low cost applications, unlike e.g. FPGA, providing ``just enough'' reconfigurability to meet design requirements.
At AKYA I contributed as a software engineer to develop a framework that synthesises RT logic from a high-level description of the hardware. My role was to design and develop algorithms and software components that expand and integrate the existing framework, as well as creating tools for testing and data visualization.}

\vspace {1em}
\textbf{DSP Lab, University of Genova}, Genova, Italy\\
\cvitem{Post Doctoral Research Fellow}{Jan 2016 - Nov 2016}
\cvitem{Ph.D. Student}{Jan 2013 - Dec 2015}
\cvitem{Research Fellow}{Oct 2012 - Dec 2012}
\expbox{During my academic experience at the DSP Labs, as Ph.D. student and then research fellow, I carried out academic (research and teaching) activity, along with projects in collaboration with SMEs and some of the key industries of Italy's communications and tech (Telecom Italia, Leonardo). My main area of research were resource allocation and mathematical optimization in communication networks and in signal processing}

\vfill
\moveleft\hoffset\vbox{\color{color1}\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
\vspace{-0.5em}
\footnotesize
The source to this CV is open and available here: \url{https://github.com/gluzzati/cv}.\\
Feel free to re-use it if you liked it!  \hfill\printversion

\end{resume}
\end{document}