\documentclass[mm, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage[T1]{fontenc}   
\usepackage[left=5mm, right=20mm, top=10mm ,bottom=10mm]{geometry}
%\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{array}
\usepackage{hyperref}


%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage[rm,sfdefault]{roboto}
\usepackage{xcolor}

\setlength{\textwidth}{5.85in} % Text width of the document
\definecolor{color1}{rgb}{0.4,0.5,0.3}% green

\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}

\newcommand{\ecvitem}[2]{{\robotocondensed #2}

}

\newcommand{\skilla}[1]{
\begin{tabular}{>{\raggedleft}m{1.6cm} l}
#1&\hspace{-0.5em}{\Large{\color{color1}$\bullet$}{\color{gray!50}$\bullet\bullet$}} \\
\end{tabular}
}
\newcommand{\skillb}[1]{
\begin{tabular}{>{\raggedleft}m{1.6cm} l}
#1&\hspace{-0.5em}{\textbf{\Large{\color{color1}$\bullet\bullet$}{\color{gray!50}$\bullet$}}} \\
\end{tabular}
}
\newcommand{\skillc}[1]{
\begin{tabular}{>{\raggedleft}m{1.6cm} l}
#1&\hspace{-0.5em}{\textbf{\Large{\color{color1}$\bullet\bullet$}{\color{color1}$\bullet$}}} \\
\end{tabular}
}

\newcommand{\expbox}[1]{\vspace{-1.8em}
\noindent\begin{tcolorbox}[boxsep=0pt,top=3pt,left=8pt,right=0pt, bottom=2pt,arc=0pt,auto outer arc,colback=color1!15,colframe=color1!10]
\begin{minipage}[r]{0.95\linewidth} 
\small
#1 
\normalsize
\end{minipage}
\end{tcolorbox}
}

\newcommand{\tinyexpbox}[1]{\vspace{-1.8em}
\noindent\begin{tcolorbox}[boxsep=0pt,top=3pt,left=8pt,right=0pt, bottom=2pt,arc=0pt,auto outer arc,colback=color1!15,colframe=color1!10]
\begin{minipage}[r]{0.95\linewidth} 
\footnotesize
#1 
\normalsize
\end{minipage}
\end{tcolorbox}
}

\newcommand{\cvitem}[2]{{\sl #1} \hfill \textbf{#2}\\}
\newcommand{\detcvitem}[3]{{\sl #1} \hfill \textbf{#2}\\{\hspace*{1em} \small \robotocondensed #3}\\}
\newcommand{\project}[5]{{\sl #1} \hfill \textbf{#2}\\ 
\textbf{Partners:} #3\\
\textbf{Decription:} \small #4\\
\textbf{My role:}\vspace{-1em} #5\par}


\newlength{\seplinewidth}
\newlength{\seplinesep}
\setlength{\seplinewidth}{1mm}
\setlength{\seplinesep}{2mm}
\newcommand*{\sepline}{%
  \par
  \vspace{\dimexpr\seplinesep+.5\parskip}%
  \cleaders\vbox{%
    \begingroup % because of color
      \color{color1}%
      \hrule width\linewidth height\seplinewidth
    \endgroup
  }\vskip\seplinewidth
  \vspace{\dimexpr\seplinesep-.5\parskip}%
}


\usepackage[most]{tcolorbox}

\usepackage{fontawesome}
\usepackage[document]{ragged2e}



\hyphenation{
  microservice
  visualization
  systems
  Python
  FastAPI
  performance
}

\begin{document}
\sloppy

\begin{resume}
\robotoslab
{ \color{color1} \Large \robotoslab Giulio Luzzati}% Your name at the top
\vspace{2em}
\sepline

\raggedleft
{\robotocondensed 
{\color{color1}\faMapMarker}~:~1b Mill Road, Haddenham, Ely, United Kingdom} \\
{\color{color1}\faPhone}~:~{\robotocondensed +44 07397 791131}\\
{\color{color1}\faEnvelope}~:~{\robotocondensed giulio.luzzati@live.it}\\
{\color{color1}\faLinkedinSquare}~:~{\url{https://it.linkedin.com/in/giulio-luzzati-9bb79245}}\\

\justify

\vspace{2em}

\sepline

\vspace{5em}

Dear Elsewhen Team,
\vspace{3em}


I would like to express my interest in the Senior Python Engineer position at Elsewhen. 
With several years of hands-on experience building scalable and maintainable systems and APIs, I believe I could be a strong addition to your team.

In my current role as DSP Team Leader, I've architected and developed Python-based systems across the full development stack.
I've designed and developed a FastAPI microservice that became the cornerstone of our company's automation infrastructure, while also building data pipelines and implementing CI/DevOps practices using Docker. 
My work includes database design, high-performance C code integration, and real-time visualization systems.

What I'm looking for in my next job is the flexibility of a remote first scheme, and the chance to apply my background to AI/ML challenges, which makes this job advert look especially relevant to me.

I have hands-on experience with PyTorch, having implemented neural networks for experimental signal processing applications, and am eager to expand my expertise in practical applications.


\vspace{2em}
Looking forward to discussing further should you find my profile of interest!

Best regards,
\vspace{3em}

Giulio


\end{resume}
\end{document}